Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-17 paper.qmd
Added labels as well for Figure 10

free(distance_points) /
  wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, two_curvy_proj_umap_model_delaunay, two_curvy_proj_umap_model_benchmark2, two_curvy_proj_umap_model, ncol = 3)

>>>>

free(distance_points) /
  wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, two_curvy_proj_umap_model_delaunay, two_curvy_proj_umap_model_benchmark2, two_curvy_proj_umap_model, ncol = 3) +
  plot_annotation(tag_levels = list(c("(a)", "(b)")))
